Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
feat: 添加 ACT 和其他算法的对比

 As shown in \cref{fig1}\textbf{(a)},the algorithm employs action chunking and temporal ensemble techniques during training. With a fixed chunk size k, the agent receives environmental observations every k steps and executes k sequential actions. This design effectively reduces historical error accumulation. To ensure motion continuity, the algorithm queries the policy at every timestep, generating overlapping predicted actions that are then smoothly blended through temporal ensemble using exponential weighting.

>>>>

As illustrated in \cref{fig1}\textbf{(a)}, ACT incorporates two key components: action chunking and temporal ensemble. With a fixed chunk size $k$, the agent receives an observation every $k$ steps and executes $k$ consecutive actions. This reduces the accumulation of errors across time. To maintain motion continuity, the policy is queried at every timestep, producing overlapping action sequences that are blended through exponential temporal ensemble.

Compared to prior imitation learning methods such as BC-ConvMLP, BeT, and RT-1, ACT demonstrates several notable improvements. BC-ConvMLP uses a simple feedforward architecture based on current image and joint inputs, without modeling temporal dependencies, which often leads to unstable behavior. BeT and RT-1 adopt Transformer architectures for temporal modeling but predict only a single action at a time, lacking structured action-level modeling. In addition, both typically discretize the action space, which limits their effectiveness in high-precision tasks. In contrast, ACT directly predicts continuous actions, and its use of action chunks and temporal blending improves both accuracy and robustness, especially in long-horizon, multi-stage robotic manipulation tasks.
